---
title: "Wine Report"
author: "Amal Alghamdi"
date: '2022-06-15'
output: html_document

knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_dir = "../"
    )
  })

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(janitor)
library(GGally)
library(here)
library(kableExtra)

```

## Introduction
This report  explores the red_wine_quality dataset, more details on the wine data will be given.

```{r, echo=FALSE}
wine <- read_csv("../data/winequality-red.csv", show_col_types = FALSE)
wine %>% 
  clean_names() -> wine
wine 
```



## Dataset
The datasets can be found  available from the UCI machine learning website ,\
Input variables (based on physicochemical tests):\
1 - fixed acidity\
2 - volatile acidity\
3 - citric acid\
4 - residual sugar\
5 - chlorides\
6 - free sulfur dioxide\
7 - total sulfur dioxide\
8 - density\
9 - pH\
10 - sulphates\
11 - alcohol\
12 - quality \
-Contain\
Rows: 1,599
 Columns: 12

```{r, echo=FALSE}
kable(head(wine,5), "html") %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```
```{r, echo=FALSE}
glimpse(wine)
summary(wine)
```
## Exploratory Data Analysis


This section exploratory data analysis will be performed via histograms. 


```{r, echo=FALSE}
ggplot(wine, aes(quality, fill = quality)) +
  geom_bar(fill = seq(1, 6, 1)) +
  geom_text(position = "stack", stat='count', aes(label=..count..), vjust = -0.5) +
  theme(plot.title=element_text(hjust=0.5)) +
  labs(x="Wine Quality",
       y="Observations",
       title = "Red Wine Quality Ratings Distribution")

```


From Figure bellow, one can see that the  density and pH  are normally distributed, as well as volatile acidity.    

```{r, echo=FALSE}
wine %>%
  keep(is.numeric) %>% 
  gather() %>% 
  ggplot(aes(value,fill=key)) +
    facet_wrap(~ key, scales = "free") +
    geom_histogram(bins=sqrt(nrow(wine))) +
    theme(legend.position="none")
    
```

## Conclusion

To sum up, from our exploratory analysis we conclude that red wine quality is strongly correlated with  alcohol and volatile acidity.












